NGO analysis

### 2022-07-24 Dashboard/NGO Analysis dashboard alpha.Rmd
KPI_OPX changing line breaks.

If desired, a copy of the analysis in html format may then be downloaded.

```{r sidebar_button}
# download
uiOutput("downloadUI")
```

@@

```{r value_boxes, include=FALSE}
# Shiny actions

  # Report Output ==============================================================

  output$downloadUI <- renderUI( {
  downloadButton("report", "Generate report")
})

  output$report <- downloadHandler(
    filename = "report.html",
    content = function(file) {
      tempReport <- file.path(tempdir(), "report.Rmd")
      file.copy("report.Rmd", tempReport, overwrite = TRUE)

      params <- list(htmlfile = input$html$datapath,
                     excelfile = input$excel$datapath,
                     start = input$start,
                     end = input$end)

      rmarkdown::render(tempReport, output_file = file,
                        params = params,
                        envir = new.env(parent = globalenv()))
    }
  )

observe({ # wait for button click

>>>>

@@

```{r value_boxes, include=FALSE}
# Shiny actions
observe({ # wait for button click
